% Add to TOC
\addcontentsline{toc}{chapter}{Curriculum vitae}

% If you want to remove page numbers
%\pagestyle{empty}


% Default settings for enumerate environment
\setenumerate{wide=0em,%
              leftmargin=*,
              labelindent=0pt,
              label=\textbullet,
              noitemsep,
              topsep=0pt,
              parsep=0pt,
              before=\rmfamily}

% Remove indentation
\setlength{\parindent}{0pt}

% Space between paragraphs
\setlength{\parskip}{6pt}

% No added spaces after periods
\frenchspacing

% For a reasonable fit
\footnotesize

\textbf{\small Curriculum Vitae\hfill\large Amama Mahmood\hfill\small May, 2020}
\begin{center}
Johns Hopkins University\\
Baltimore, Maryland 21218, USA\\
(+1) 410.508.5727\\
{\color{blue} \ul{\sffamily\textit{amahmo11@jhu.edu}}}\\
{\color{blue} \ul{\sffamily\textit{https://amamamahmood.wixsite.com/website}}}
\end{center}

% change font 
\sffamily

\textbf{EDUCATION AND DEGREES}

\ul{2018--Present} Graduate student, Fulbright Scholar
Laboratory for Computational Sensing $+$ Robotics (LCSR)\\
Johns Hopkins University

\ul{2013--2017} Undergraduate student,
Department of Electrical Engineering,
National University of Sciences and Technology


\textbf{RESEARCH EXPERIENCE}

\textit{Johns Hopkins University, Intuitive Computing Lab}\\
\textit{LCSR and Department of Computer Science\hfill(August 2019-Present)}\\
\textbf{\rmfamily Graduate Student in the laboratory of \ul{Dr. Chien-Ming Huang}}

\begin{enumerate}
\item Developed a perception system to track user's progress in 3D block building spatial task.
\item Developed feedback system to assist user in completion of 3D block building task. 
\item Designed robot behaviour.
\end{enumerate}

\textit{Johns Hopkins University, Teleoperaction group}\\
\textit{LCSR and Department of Computer Science \hfill(March 2019-December, 2019)}\\
\textbf{\rmfamily Graduate Student in the laboratory of \ul{Dr. Peter Kazanzides}}

\begin{enumerate}
\item Worked on satellite servicing mission project. 
\item Used computer vision techniques on video stream of blade cutting through multilayer insulation hat on the satellite body to get an estimate of forces acting on blade.
\end{enumerate}

\textit{Signal, Image and Video Processing lab at Lahore University of Management Sciences, Lahore, Pakistan \hfill(October 2017-July 2018)}\\
\textbf{\rmfamily Post-baccalaureate Researcher in the laboratory of \ul{Dr. Nadeem Khan}}

\begin{enumerate}
\item Worked on applications of brain computer interfacing.
\item Presented feasibility analysis of existing multi-class motor imagery systems for real-time applications. 
\end{enumerate}

\textit{Neuro-informatics lab, SEECS-NUST, Pakistan\hfill(June 2016-September 2017)}\\
\textbf{\rmfamily A previous position in the laboratory of \ul{Dr. Awais Mehmood Kamboh}}

\begin{enumerate}
\item Worked on brain computer interface to drive a telepresence robot with motor imagery EEG commands. This assembly can be used as a stroke rehabilitation system.
\end{enumerate}

\textit{Sigma lab, SEECS-NUST, Pakistan\hfill(Feb 2016-July 2017)}\\
\textbf{\rmfamily A previous position in the laboratory of \ul{Dr. Hassan Aqeel}}

\begin{enumerate}
\item Worked on Machine Learning and Automatic Speech Recognition (ASR) using Kaldi.
\end{enumerate}


\textit{SMART lab, SEECS-NUST, Pakistan\hfill(November 2015-June 2017)}\\
\textbf{\rmfamily A previous position in the laboratory of \ul{Dr. Osman Hasan}}

\begin{enumerate}
\item Worked on SmartSIM, a virtual reality simulator for training in laparoscopic surgery.
\item Worked on Phantom Omni, a forced feedback haptic device.
\end{enumerate}

\textbf{KEY SKILLS}

\textbf{\rmfamily Programming}

\textrm{\noindent Python, C, C++, MATLAB, Verilog HDL, G, Assembly and Embedded C for Microcontrollers}

\textbf{\rmfamily Simulation}
\textrm{\noindent Gazebo, Rviz, Cadence, Simulink, Orcad Pspice, AutoCAD, Proteus, Keil, Xilinx, MPLAB, Arduino, ADS, OpenVibe}

\textbf{\rmfamily Miscellaneous}
\textrm{\noindent ROS, Microsoft Windows, Microsoft Office, Ubuntu, LaTex, Inkscap}

\textbf{TEACHING EXPERIENCE}

\textit{Johns Hopkins University, LCSR and Department of Computer Science\hfill(January 2020-May 2020)}\\
\textbf{\rmfamily Teaching Assistant}
\begin{enumerate}
\item Graduate Student Instructor for Human-Robot Interaction 
\end{enumerate}


\textbf{PUBLICATIONS}

% change font back to roman
\rmfamily

{\color{blue} \ul{Classification of Multi-Class Motor Imagery EEG using Four Band Common Spatial Pattern}} 
\textbf{A. Mahmood}, R. Zainab, R.B. Ahmad, M. Saeed and 
A.M. Kamboh. \textit{39th Annual International Conference of the IEEE Engineering in Medicine and Biology Society} (2017).

{\color{blue} \ul{SmartSIM - A Virtual Reality Simulator for Laparoscopy Training using a Generic Physics Engine}} 
Z.A. Khan, N. Kamal, A. Hameed, \textbf{A. Mahmood}, R. Zainab, B. Sadia, S.B. Mansoor and 
O. Hasan. \textit{The International Journal of Robotics and Computer Aided Surgery} \textbf{13}. e1771 (2017).

